### 2015-07-12 narrative/evaluation.tex
eva.

%I dont think this table is right. Knowledge is our independent variable
%and predictability is our dependent variable
\begin{table}[ht]
\small
\centering
\caption{Guiding Principles}
\label{table:eval}
\begin{tabular}{ | p{1.4in} | p{2in} | p{2.5in} | }
  \hline
  {\bf Principle/Metric}                   & {\bf User perspective metric}   & {\bf System perspective metric }\\ \hline
  {\bf Knowledge-centric system}           & More knowledge = faster access to higher quality data &  More knowledge = better resource utilization across the entire hierarchy \\ \hline
  {\bf Predictable Performance Accuracy}   & More predictability = better quality of data &  Accuracy of the time bounds across multiple layers of the storage hierarchy wrote/read in time constrained situations\\ \hline
\end{tabular}
\vspace{-2ex}
\normalsize
\end{table}

>>>>

%I dont think this table is right. Knowledge is our independent variable
%and predictability is our dependent variable
\begin{table}[ht]
\small
\centering
\caption{Guiding Principles}
\label{table:eval}
\begin{tabular}{ | p{1.4in} | p{2in} | p{2.5in} | }
  \hline
  {\bf Principle/Metric}                   & {\bf User perspective metric}   & {\bf System perspective metric }\\ \hline
  {\bf Knowledge-centric system}           & More knowledge = faster access to higher quality data &  More knowledge = better resource utilization across the entire hierarchy \\ \hline
  {\bf Predictable Performance and Accuracy}   & More predictability = better quality of data &  Accuracy of the time bounds across multiple layers of the storage hierarchy wrote/read in time constrained situations\\ \hline
\end{tabular}
\vspace{-2ex}
\normalsize
\end{table}
